---
title: "retriever"
author: "Thi Pham and Somaya Khoda Bakhsh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

##Introduction

The **retriever** package uses the google geocode API to provide address and coordinates. It consists two main functions: 

1. address
2. coordinates

To use both functions, it is **required to have the package httr installed.** 

## Functions usage

### address function

This function provides the user with the address of a given a set of coordinates. The funtion uses the google geocode API to retrieve the result.

The input is **latlong**, a character string that includes the latitude and the longitude.

The function returns a dataframe containing full address and coordinates:

```{r, fig.show='hold', message=FALSE}
library(retriever)
head(address("41.40450 2.17429"), n = 5)
tail(address("58.39783 15.57600"), n = 5)
```


###coordinates function

This function provides the user with the coordinates of a given address. The function uses the google geocode API to retrieve the result.

The input is **address**, a character string that includes address components.

If the address has partial match, different locations with their full names and  coordinates will be retrieved as a dataframe:

```{r, fig.show='hold', message=FALSE}
library(retriever)
coordinates("Parliament House, Australia")
coordinates("Eiffel Tower, Paris")
```



